Simulation study in fjords

### 2024-05-08 R/simulation_study/fjords/simulation_study_fjords.Rmd
update simulation study

#auxiliary function to simulate from RACVM with specified smooth function for omega
source("CVM_functions.R")
```

@@

```{r}
#number of batch
N_BATCH=5

@@

#duration of each track in hour
TMAX=0.5*24

@@

# Set the path to the directory containing the data
par_dir=dirname(dirname(getwd())) #parent directory 
greenland_data_path <- file.path(par_dir,"Data", "Greenland")

@@

@@

Dshore=seq(from=0.1,to=2,length.out=30)
theta=seq(from=-pi,to=pi,length.out=30)
grid<- as.data.frame(expand.grid(Dshore,theta))
colnames(grid)=c("DistanceShore","theta")
true_tau=matrix(ftau_bump(grid),30,30)
true_omega=matrix(fomega(grid),30,30)

@@

data_fjords_hf_ne <- foreach(k=1:N_BATCH,.packages=c("progress","MASS","sf","foreach")) %dopar% {
  data=foreach (i=1:N_ID,.combine='rbind') %do% {

    res=sim_theta_CRCVM(ftau_constant,fomega,fnu_constant,log_sigma_obs=log(sigma_obs),v0,x0[i,],times_hf,land=land,verbose=FALSE)

    data_sim=res$sim
    data_sim$ID=factor(rep(i,length(data_sim$y1)))
    data_shore=res$shore[,c("p1","p2")]
    cbind(data_sim,data_shore)
  }
  data 
}

@@

names(data_fjords_hf_ne)=paste("BATCH",1:N_BATCH,sep="")
```

@@

```{r percentage of low error samples that reached land}
count=0
for (k in 1:length(names(data_fjords_hf_ne))) {

  data=data_fjords_hf_ne[[paste("BATCH",k,sep="")]]
  for (id in unique(data$ID)) {
    sub_data=data[data$ID==id,]
    if (nrow(sub_data) < n_hf) {
      count=count+1
      cat(paste("BATCH",k,sep=""),":",id,"\n",sep=" ")
    }
  }
}
cat(count/(N_BATCH*N_ID)*100,"percent of the samples reached land")
```

@@

plot_samples_fjords_hf_ne=ggplot()+geom_sf(data=land$geometry,fill=NA)+coord_sf(datum=st_crs(32626))+
  geom_point(data=data_fjords_hf_ne$BATCH1,mapping=aes(y1,y2,color=ID),size=0.1)+
  geom_path(data=data_fjords_hf_ne$BATCH1,mapping=aes(y1,y2,color=ID),size=0.1)+
  geom_point(data = data_fjords_hf_ne$BATCH1%>% filter(!duplicated(ID)),
             aes(x = y1, y = y2), shape = 3, size = 4, col = "red")+
  xlab("x") + ylab("y")

ggsave(filename="samples_fjords_hf_ne_omega.png",plot=plot_samples_fjords_hf_ne,width=10,height=5)
ggplotly(plot_samples_fjords_hf_ne)
```

>>>>

#auxiliary function to simulate from RACVM with specified smooth function for omega
par_dir=dirname(getwd())
source(file.path(par_dir,"CVM_functions.R"))
```

@@

@@

#duration of each track in hour
TMAX=5*24

@@

# Set the path to the directory containing the data
par_dir=dirname(dirname(dirname(getwd()))) #parent directory 
greenland_data_path <- file.path(par_dir,"Data", "Greenland")

@@

fomega_fast=function(cov_data,D0=0.05,omega0=120*pi,lambda=2,kappa=0.2) {
    Dshore=cov_data$DistanceShore
    theta=cov_data$theta
    if (is.null(Dshore)){
      Dshore=1/cov_data$ExpShore
    }
    coeff=exp(-kappa*(Dshore/D0)^2)
    omega=omega0/2*(tanh(lambda*(theta+pi/2-atanh(-0.9)/lambda))+tanh(lambda*(theta-(pi/2-atanh(-0.9)/lambda))))*coeff
    return(omega)
}

@@

Dshore=seq(from=0.01,to=2,length.out=30)
theta=seq(from=-pi,to=pi,length.out=30)
grid<- as.data.frame(expand.grid(Dshore,theta))
colnames(grid)=c("DistanceShore","theta")
true_tau=matrix(ftau_bump(grid),30,30)
true_omega=matrix(fomega_fast(grid),30,30)

@@

data_fjords_hf_ne <- foreach (i=1:N_ID,.combine='rbind',.packages=c("progress","MASS","sf")) %dopar% {

    res=sim_theta_CRCVM(ftau_constant,fomega_fast,fnu_constant,log_sigma_obs=log(sigma_obs),v0,x0[i,],times_hf,land=land,verbose=FALSE)

    data_sim=res$sim
    data_sim$ID=factor(rep(i,length(data_sim$y1)))
    data_shore=res$shore[,c("p1","p2")]
    cbind(data_sim,data_shore)
}

@@

@@

```{r percentage of low error samples that reached land}
count=0
for (id in unique(data_fjords_hf_ne$ID)) {
  sub_data=data_fjords_hf_ne[data_fjords_hf_ne$ID==id,]
  if (nrow(sub_data) < n_hf) {
    count=count+1
    cat(paste("BATCH",k,sep=""),":",id,"\n",sep=" ")
  }
}

cat(count/(N_ID)*100,"percent of the samples reached land")
```

@@

plot_samples_fjords_hf_ne=ggplot()+geom_sf(data=land$geometry,fill=NA)+coord_sf(datum=st_crs(32626))+
  geom_point(data=data_fjords_hf_ne,mapping=aes(y1,y2,color=ID),size=0.1)+
  geom_path(data=data_fjords_hf_ne,mapping=aes(y1,y2,color=ID),size=0.1)+
  geom_point(data = data_fjords_hf_ne%>% filter(!duplicated(ID)),
             aes(x = y1, y = y2), shape = 3, size = 4, col = "red")+
  xlab("x") + ylab("y")

ggsave(filename="samples_fjords_hf_ne_omega.png",plot=plot_samples_fjords_hf_ne,width=10,height=5)
ggplotly(plot_samples_fjords_hf_ne)
```
```{r plot subsampled data}

data_fjords_lf_ne=data_fjords_hf_ne[seq(1,length(data_fjords_hf_ne$time),by=50),]
plot_samples_fjords_lf_ne=ggplot()+geom_sf(data=land$geometry,fill=NA)+coord_sf(datum=st_crs(32626))+
  geom_point(data=data_fjords_lf_ne,mapping=aes(y1,y2,color=ID),size=0.1)+
  geom_path(data=data_fjords_lf_ne,mapping=aes(y1,y2,color=ID),size=0.1)+
  geom_point(data = data_fjords_lf_ne%>% filter(!duplicated(ID)),
             aes(x = y1, y = y2), shape = 3, size = 4, col = "red")+
  xlab("x") + ylab("y")

ggsave(filename="samples_fjords_lf_ne_omega.png",plot=plot_samples_fjords_lf_ne,width=10,height=5)
ggplotly(plot_samples_fjords_lf_ne)
```
